### 2021-05-04 Draft.tex
init commit rough Draft for paper and outlining perspectiv.

\documentclass[12pt, a4paper]{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ngerman}
\usepackage[ansinew]{inputenc}
\usepackage[left=2.5cm,top=2.5cm]{geometry}

\begin{document}
    \tableofcontents

\section{Abstract}
This paper outlines the positiv and negatives aspects of Peer-Studying.
Additionaly an transfer of the findings to an eLearning-Enviroment will be made. 
Futhermore a possible implementation will be presented.
Subsequently an analysis of said implementation  will be provided as well as suggestions
for improvements.

\section{Introduction}
\section{Materials and Methodes}
\section{Results}
\section{Discussion}
\section{Conclusion}
\section{Refernces}
\end{document}

### 2021-05-05 Draft.tex
Update Draft.tex
Update Draft.tex
Abstract angepasst und titel hinzu gefügt.

@@
 
+\section{Title: Observing Motivation in eLearning facing real world problems}
+
 \section{Abstract}
-This paper outlines the positiv and negatives aspects of Peer-Studying.
-Additionaly an transfer of the findings to an eLearning-Enviroment will be made. 
-Futhermore a possible implementation will be presented.
-Subsequently an analysis of said implementation  will be provided as well as suggestions
-for improvements.
+In the current light of the pandemic the worldwide use of eLearning-Software experienced an unpresented boom.
+We challenge the question how technical problems influence the motivation and stress of students in an eLearning-Environment.
+To provide answers an online questionnaire with deliberate technical difficulties was constructed which monitored the behaviour of the test subjects.
 

### 2021-07-06 Draft.tex
abstract finished

--- 2021-05-04 Draft.tex
@@
-\documentclass[12pt, a4paper]{article}
+%\documentclass[12pt, a4paper]{article}
+\documentclass[runningheads]{llncs}
 \usepackage{graphicx}
@@
 \usepackage{amssymb}
-\usepackage{ngerman}
+% \usepackage{ngerman}
 \usepackage[ansinew]{inputenc}
@@
 
+\renewcommand\UrlFont{\color{blue}\rmfamily}
+
 \begin{document}
-    \tableofcontents
 
-\section{Abstract}
-This paper outlines the positiv and negatives aspects of Peer-Studying.
-Additionaly an transfer of the findings to an eLearning-Enviroment will be made. 
-Futhermore a possible implementation will be presented.
-Subsequently an analysis of said implementation  will be provided as well as suggestions
-for improvements.
+\title{The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}}
+
+\author{Lucas Laub\inst{1}\orcidID{6621331} \and
+Second Author\inst{2}\orcidID{1111-2222-3333-4444}}
+
+\institute{Goethe University Frankfurt, 60323 Frankfurt a. Main, Germany.}
+
+\maketitle
+
+\begin{abstract}
+In the current light of the pandemic the worldwide use
+of eLearning-Software experienced an unpresented boom.
+We state the question how commen network problems influence
+the academic performance in an eLearning-Environment.
+To provide answers an online questionnaire with deliberate
+technical difficulties was constructed. Evaluating the performance
+of the test and controll group did not show any significant
+differences.
+\keywords{eLearning  \and Online-Learning \and academic performance.}
+\end{abstract}
 

### 2021-07-07 Draft.tex
Adding methodes

@@
 \section{Materials and Methodes}
+\subsection{Preperations}
+The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
+This software allowed the tracking of {\itshape technical problems} introduced by
+the software itself as well as the points and answers scored by each participant.
+Additianaly a room with an adequat number of computers with a fiber-connection
+to the server are needed, to rule out uncontrolled network problems.
+Half of the cumputers are manipulated and simulate the network problems with the
+use of the software.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{UML Prototyp.PNG}
+    \caption{A logic flow chart , representing how an implementation could operate.
+    The black circle is the user interacting with the software. The webside would
+    consist of two parts. A frontend handling user interaction and the creation of {\itshape bugs}.
+    The backend responsible for saving the collected data and ensuring the frontend
+    remains operationale.} \label{fig1}
+\end{figure}
+
+\subsection{Participants}
+The participants are students of the 5 grade and consist of two groups the controll group [CG] and
+the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
+It should be ensured that both groups prior to the experiment perform academicly similar, if not a
+comparison post experiment will be difficult.
+
 \section{Results}

### 2021-07-08 code/generate/rnd.py
add generate code + bug fix

@@ -1,0 +1,80 @@
+import numpy as np
+from numpy.core.fromnumeric import std
+from scipy.stats.stats import ttest_ind
+
+np.random.seed(42)
+# create array of controllgroup
+controll_group_f = np.random.randint(0, 100, (1, 50), dtype=np.int32)
+controll_group_m = np.random.randint(0, 100, (1, 50), dtype=np.int32)
+
+# create array of errorgroup
+controll_error_f = np.random.randint(0, 100, (1, 50), dtype=np.int32)
+controll_error_m = np.random.randint(0, 100, (1, 50), dtype=np.int32)
+
+# calc standart deviation and mean
+gf = (np.mean(controll_group_f), np.std(controll_group_f))
+gm = (np.mean(controll_group_m), np.std(controll_group_m))
+ef = (np.mean(controll_error_f), np.std(controll_error_f))
+em = (np.mean(controll_error_m), np.std(controll_error_m))
+
+print(f"The mean of the controllgroup (50f): {gf[0]} with an SD: {gf[1]}")
+print(f"The mean of the controllgroup (50m): {gm[0]} with an SD: {gm[1]}")
+print(f"The mean of the errorgroup (50f): {ef[0]} with an SD: {ef[1]}")
+print(f"The mean of the errorgroup (50m): {em[0]} with an SD: {em[1]}")
+
+# calc t-test
+
+# controllgroup vs errorgroup
+a = ttest_ind(
+    controll_group_f + controll_group_m, controll_error_f + controll_error_m, 1
+)
+print(
+    f"The values for controllgroup (50f/50m) vs errorgroup (50f/50m) are t-value: {a[0]} and p-value: {a[1]}"
+)
+
+# controll with in the groups
+b = ttest_ind(controll_group_f, controll_group_m, 1)
+c = ttest_ind(controll_error_f, controll_error_m, 1)
+print(
+    f"The values for controllgroup (50f) vs controllgroup (50m) are t-value: {b[0]} and p-value: {b[1]}"
+)
+print(
+    f"The values for errorgroup (50f) vs errorgroup (50m) are t-value: {c[0]} and p-value: {c[1]}"
+)
+
+
+# values between the groups same sex
+d = ttest_ind(controll_group_f, controll_error_f, 1)
+e = ttest_ind(controll_group_m, controll_error_m, 1)
+
+print(
[…]

### 2021-07-08 code/routers/questions.py

@@ -57,8 +57,8 @@ async def get_next_question(
     if raise_error is not False:
         error_codes = [400, 401, 403, 404, 408]
         code = random.choice(error_codes)
-        db["log"].inster_one(
-            {"username": current_user.username, "code": code, "question_id": (id)}
+        await db.log.insert_one(
+            ({"username": current_user.username, "code": code, "question_id": id})
         )
         if code == 408:
             time.sleep(30)
@@ -83,3 +83,7 @@ async def push_question(
     new_answere = await db["answere"].insert_one(answere)
     lookup = await db["answere"].find_one({"_id": new_answere.inserted_id})
     return JSONResponse(status_code=status.HTTP_201_CREATED, content=lookup)
+
+
+# db.user.updateOne({username: "seminar"},{$set: {"question_id": "1"}})
+# dimitri@dipf.de     drachsler@em.uni-frankfurt.de in cc.

### 2021-07-08 Addition.tex
Not finished yet, but in progress

\documentclass[12pt, a4paper]{article}
%\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{ngerman}
\usepackage[ansinew]{inputenc}
\usepackage[left=2.5cm,top=2.5cm]{geometry}
\usepackage[section]{placeins}

\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\title{The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}}

\author{Lucas Laub \inst{1}\orcidID{6621331} \and
Alexander Perekhrest \inst{2}\orcidID{6379748}}

\institute{Goethe University Frankfurt, 60323 Frankfurt a. Main, Germany.}

\maketitle

\begin{abstract}
In the current light of the pandemic the worldwide use
of eLearning-Software experienced an unpresented boom.
We state the question how common network problems influence
the academic performance in an eLearning-Environment.
To provide answers an online questionnaire with deliberate
technical difficulties was constructed. Evaluating the performance
of the test and control group did not show any significant
differences.
\keywords{eLearning  \and Online-Learning \and academic performance.}
\end{abstract}

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, it's important to know the things that come with being on such a platform and the possible influences those things might have on the method.\\\\
In day-to-day usage of online platforms and services it's not uncommon to face some issues, whether it's execution, connectivity and so on. E-Learning-platforms are not particularly different to those. Therefore, we want to discuss, in this paper, to which extent these problems can influence the test-results of being on such a 'issue-infected' platform in contrast to a well running platform with no issues.\\\\
We tried to focus on the most frequent issues we faced in our experience of browsing on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\

\section{Materials and Methods}
\subsection*{Preparations}
The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
This software allowed the tracking of {\itshape technical problems} introduced by
the software itself as well as the points and answers scored by each participant.
Additionally a room with an adequate number of computers with a fiber-connection
to the server are needed, to rule out uncontrolled network problems.
Half of the computers are manipulated and simulate the network problems with the
use of the software.

\begin{figure}[h]
    \includegraphics[width=\textwidth]{UML Prototyp.PNG}
    \caption{A logic flow chart , representing how an implementation could operate.
    The black circle is the user interacting with the software. The website would
    consist of two parts. A front-end handling user interaction and the creation of {\itshape bugs}.
    The back-end responsible for saving the collected data and ensuring the front-end
    remains operational.} \label{fig1}
\end{figure}

\subsection*{Participants}
The participants are students of the 5th grade and consist of two groups the control group [CG] and
the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
It should be ensured that both groups prior to the experiment perform academically similar, if not a
comparison post experiment will be difficult.
\newpage
\section{Results}
\begin{figure}[h]
    \includegraphics[width=\textwidth]{results.PNG}
\end{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{all.png}
\end{center}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{female.png}
    \includegraphics[width=.5\textwidth]{male.png}
    \includegraphics[width=.5\textwidth]{fsav_msav.png}
    \includegraphics[width=.5\textwidth]{ferr_merr.png}
\end{figure}
\begin{figure}[h]
    \includegraphics[width=.5\textwidth]{fsav_merr.png}
    \includegraphics[width=.5\textwidth]{msav_ferr.png}
\end{figure}

\section{Discussion}
\section{Conclusion}
\section{References}
\end{document}

### 2021-07-08 Addition.tex
Update Addition.tex

@@
 
+\subsection*{Implementation}
+We implemented a possible back-end, which can be used offline. You can find it 
+at \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}.
 \subsection*{Participants}
@@
     \includegraphics[width=.5\textwidth]{fsav_msav.png}
-    \includegraphics[width=.5\textwidth]{ferr_merr.png}
+    \includegraphics[width=.5\textwidth]{ferr_merr.png}\\\\\\\\
 \end{figure}
@@
     \includegraphics[width=.5\textwidth]{msav_ferr.png}
+    \caption{These are the box-plots where we compared the different outcomes with each other. There were 100 reachable points.}
 \end{figure}
+We also calculated the t- and p-values to see which two groups have the most significant differences.
+We saw the biggest difference between the females from the control group and error group, where we got a t-value of 0.949 and a p-value of 0.345.
+This makes the relationship between error and non-error groups not significant enough, because their p-value is larger than 0.05.
 
@@
 \section{References}
+\url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}
 \end{document}

### 2021-07-08 Addition.tex
Update Addition.tex

@@
 \section{Introduction}
-When trying to transfer an already existing method on a relatively new platform, it's important to know the things that come with being on such a platform and the possible influences those things might have on the method.\\\\
-In day-to-day usage of online platforms and services it's not uncommon to face some issues, whether it's execution, connectivity and so on.
-E-Learning-platforms are not particularly different to those.
-Therefore, we want to discuss, in this paper, to which extent these problems can influence the test-results of being on such a 'issue-infected' platform in contrast to a well running platform with no issues.\\\\
-We tried to focus on the most frequent issues we faced in our experience of browsing on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
+When trying to transfer an already existing method on a relatively new platform, 
+it's important to know the things that come with being on such a platform and the 
+possible influences those things might have on the method.\\\\
+In day-to-day usage of online platforms and services it's not uncommon to face some 
+issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
+particularly different to those. Therefore, we want to discuss, in this paper, to 
+which extent these problems can influence the test-results of being on such an 
+'issue-infected' platform in contrast to a well running platform with no issues.\\\\
+We tried to focus on the most frequent issues we faced in our experience of browsing 
+on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
+(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
 
@@
 We also calculated the t- and p-values to see which two groups have the most significant differences. 
-We saw the biggest difference between the females from the control group and error group, where we got a t-value of 0.949 and a p-value of 0.345.
-This makes the relationship between error and non-error groups not significant enough, because their p-value is larger than 0.05.
+We saw the biggest difference between the females from the control group and error group, where we 
+got a t-value of 0.949 and a p-value of 0.345. This makes the relationship between error and 
+non-error groups not significant enough, because their p-value is larger than 0.05.
 

### 2021-07-08 Draft.tex
Update

@@
 \usepackage{amssymb}
+\usepackage{capt-of}
 % \usepackage{ngerman}
@@
 \author{Lucas Laub\inst{1}\orcidID{6621331} \and
-Second Author\inst{2}\orcidID{1111-2222-3333-4444}}
+Alexander Perekhrest \inst{2}\orcidID{6379748}}
 
@@
 \section{Introduction}
+When trying to transfer an already existing method on a relatively new platform, 
+it's important to know the things that come with being on such a platform and the 
+possible influences those things might have on the method.\\\\
+
+In day-to-day usage of online platforms and services it's not uncommon to face some 
+issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
+particularly different to those. Therefore, we want to discuss, in this paper, to 
+which extent these problems can influence the test-results of being on such an 
+'issue-infected' platform in contrast to a well running platform with no issues.\\\\
+
+We tried to focus on the most frequent issues we faced in our experience of browsing 
+on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
+(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
+
 \section{Materials and Methodes}
@@
 
+\newpage
 \section{Results}
+The results are displayed in chronological order of the analysis, there is
+no emphisis on the significans given by the order itself.
+
+\subsection{Controll Group vs Error Group}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50f/50m) and
+        the error group (50f/50m).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig2}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50f/50m) the error group (50f/50m).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group & error group \\
+        \hline
+        median & 53.0&43.5 \\
+        \hline
+        standart deviation & 29.278&29.826 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.728} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.467} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group Female vs Error Group Female}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50f) and
+        the error group (50f).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig3}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50f) the error group (50f).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group & error group \\
+        \hline
+        median & 55.5&40.0 \\
+        \hline
+        standart deviation & 27.85&30.933 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.949} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.345} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group Male vs Error Group Male }
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50m) and
+        the error group (50m).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig4}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50m) the error group (50m).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group & error group \\
+        \hline
+        median & 52.5&50.5 \\
+        \hline
+        standart deviation & 30.638&28.495 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.08} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.936} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group vs Error Group}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50f) and
+        the controll group (50m).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig5}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50f) the controll group (50m).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group(f) & controll group(m) \\
+        \hline
+        median & 55.5&52.5 \\
+        \hline
+        standart deviation & 27.85&30.638 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.101} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.919} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group vs Error Group}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the error group (50f) and
+        the error group (50m).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig6}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the error group (50f) the error group (50m).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & error group & error group \\
+        \hline
+        median & 40.0&50.5 \\
+        \hline
+        standart deviation & 30.933&28.495 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{- 0.759} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.45} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group vs Error Group}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50f) and
+        the error group (50m).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig7}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50f) the error group (50m).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group & error group \\
+        \hline
+        median & 55.5&50.5 \\
+        \hline
+        standart deviation & 27.85&28.495 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.19} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.85} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
+\subsection{Controll Group vs Error Group}
+\begin{figure}
+    \begin{minipage}{0.45\textwidth}        
+        \includegraphics[width=\textwidth]{code/generate/all.png}
+        \caption{The colored squares in the boxplot displays
+        the upper and lower quartile of points earned by the controll group (50m) and
+        the error group (50f).The green line marks the mean of all datapoints in the group.
+        The gray line marks the median  of the given group.} \label{fig8}
+    \end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+\captionof{table}{The calculated median, standart deviation and t, p-values
+    for the controll group (50m) the error group (50f).
+    The t,p-values were calculated by using a two-sided t-test.}
+\begin{tabular}[]{| c | c | c |}
+        \hline
+        & controll group & error group \\
+        \hline
+        median & 52.5&40.0 \\
+        \hline
+        standart deviation & 30.638&30.933 \\
+        \hline
+        t-value & \multicolumn{2}{c|}{0.81} \\
+        \hline
+        p-value & \multicolumn{2}{c|}{0.42} \\
+        \hline            
+\end{tabular}
+\end{minipage}
+\end{figure}
+
 \section{Discussion}

### 2021-07-08 Addition.tex
Update Addition.tex

--- 2021-07-08 Addition.tex
@@
+Skip to content
+Search or jump to…
+
+Pull requests
+Issues
+Marketplace
+Explore
+
+@mevv2 
+UebeI2lauf
+/
+insertcreativeName
+1
+00
+Code
+Issues
+Pull requests
+Actions
+Projects
+Wiki
+Security
+Insights
+insertcreativeName/Addition.tex
+@mevv2
+mevv2 Update Addition.tex
+Latest commit e7bd3b9 now
+ History
+ 1 contributor
+109 lines (96 sloc)  4.99 KB
+
 \documentclass[12pt, a4paper]{article}
@@
 \section{Introduction}
-When trying to transfer an already existing method on a relatively new platform, it's important to know the things that come with being on such a platform and the possible influences those things might have on the method.\\\\
-In day-to-day usage of online platforms and services it's not uncommon to face some issues, whether it's execution, connectivity and so on.
-E-Learning-platforms are not particularly different to those.
-Therefore, we want to discuss, in this paper, to which extent these problems can influence the test-results of being on such a 'issue-infected' platform in contrast to a well running platform with no issues.\\\\
-We tried to focus on the most frequent issues we faced in our experience of browsing on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
+When trying to transfer an already existing method on a relatively new platform, 
+It's important to know the things that come with being on such a platform and the 
+possible influences those things might have on the method.\\\\
+In day-to-day usage of online platforms and services it's not uncommon to face some 
+issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
+particularly different to those. Therefore, we want to discuss, in this paper, to 
+which extent these problems can influence the test-results of being on such an 
+'issue-infected' platform in contrast to a well running platform with no issues.\\\\
+We tried to focus on the most frequent issues we faced in our experience of browsing 
+on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
+(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors', because things like lagging or 100ms more or less ping time are in our case of mostly texts and pictures not as important as those client errors.\\\\
 
@@
 We also calculated the t- and p-values to see which two groups have the most significant differences. 
-We saw the biggest difference between the females from the control group and error group, where we got a t-value of 0.949 and a p-value of 0.345.
-This makes the relationship between error and non-error groups not significant enough, because their p-value is larger than 0.05.
+We saw the biggest difference between the females from the control group and error group, where we 
+got a t-value of 0.949 and a p-value of 0.345. This makes the relationship between error and 
+non-error groups not significant enough, because their p-value is larger than 0.05.
 
 \section{Discussion}
+As we can see, the results show not much significance under our circumstances.Even though we cannot a significance, we can see slight worsening of the average scores in the error groups than to the control group.
+But we don't have to forget, that this was a short term test (for example 1 hour) and we didn't include that many variables like time, age and so on.
+Having such problem-infected websites and platforms can be very frustrating in the long run.
+Unfortunately, we couldn't recreate this scenario.
+It would be very interesting to see, how much significance such things like errors will show  in a long run with more variables included.
 \section{Conclusion}

### 2021-07-08 Addition.tex
Update Addition.tex

@@
-Skip to content
-Search or jump to…
-
-Pull requests
-Issues
-Marketplace
-Explore
-
-@mevv2 
-UebeI2lauf
-/
-insertcreativeName
-1
-00
-Code
-Issues
-Pull requests
-Actions
-Projects
-Wiki
-Security
-Insights
-insertcreativeName/Addition.tex
-@mevv2
-mevv2 Update Addition.tex
-Latest commit e7bd3b9 now
- History
- 1 contributor
-109 lines (96 sloc)  4.99 KB
-
 \documentclass[12pt, a4paper]{article}
@@
 \section{Discussion}
-As we can see, the results show not much significance under our circumstances.Even though we cannot a significance, we can see slight worsening of the average scores in the error groups than to the control group.
-But we don't have to forget, that this was a short term test (for example 1 hour) and we didn't include that many variables like time, age and so on.
-Having such problem-infected websites and platforms can be very frustrating in the long run.
-Unfortunately, we couldn't recreate this scenario.
+As we can see, the results show not much significance under our circumstances.
+Even though we cannot see a significance, we can see slight worsening of the average scores in the error groups than to the control group.
+But we don't have to forget, that this was a short term test (for example 1 hour exam) and we didn't include that many variables like time, age and so on.
+Having such problem-infected websites and platforms can be very frustrating in the long run and may make the decline of performance much worse, than we've seen here in our scenario of having to enter the 'exam' one time only.
+Unfortunately, we couldn't recreate the long-term-scenario due to its complexity and sheer number of variables.
+\section{Conclusion}
+In this paper we could clearly see the impact of platform-issues on the students performance in an exam-scenario and it's not that significant.
+There might still be certain aspect of long-term-effects,
+which we couldn't simulate due to our circumstances, because there was a slight worsening happening when comparing our outcomes.
 It would be very interesting to see, how much significance such things like errors will show  in a long run with more variables included.
-\section{Conclusion}
+\\\\
+Don't neglect setting up your server properly and running it smoothly, so your students will thank you for that with better results (in short-term).
+
 \section{References}

### 2021-07-08 Draft.tex
Almost done

@@
 \usepackage{capt-of}
+\usepackage{multicol}
+\usepackage{aliascnt}
 % \usepackage{ngerman}
@@
 technical difficulties was constructed. Evaluating the performance
-of the test and controll group did not show any significant
+of the test and control group did not show any significant
 differences.
@@
 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
+\newpage
+\section{Materials and Methodes}
+\subsection{Participants}
+The participants are students of the end of the 4 grade and consist of two groups the control group [CG] and
+the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
+It should be ensured that both groups prior to the experiment perform academicly similar, if not a
+comparison post experiment will be difficult. Students of the 5th grade have the benefit of the
+already finished primary school. Which ensures experience in simple problem solving and
+reading comprehension. Futhermore in 4th grade we can still observe all academic capabilitys
+since the division of students happens in 5th grade.
 
-\section{Materials and Methodes}
 \subsection{Preperations}
@@
 
-\subsection{Participants}
-The participants are students of the 5 grade and consist of two groups the controll group [CG] and
-the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
-It should be ensured that both groups prior to the experiment perform academicly similar, if not a
-comparison post experiment will be difficult.
-
-\newpage
+\clearpage
 \section{Results}
@@
 
-\subsection{Controll Group vs Error Group}
-\begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+\subsection{Control Group(50f/50m) vs Error Group(50f/50m)}
+\begin{figure}[!h]
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50f/50m) and
+        the upper and lower quartile of points earned by the control group (50f/50m) and
         the error group (50f/50m).The green line marks the mean of all datapoints in the group.
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50f/50m) the error group (50f/50m).
+    for the control group (50f/50m) the error group (50f/50m).
     The t,p-values were calculated by using a two-sided t-test.}
@@
         \hline
-        & controll group & error group \\
+        & control group & error group \\
         \hline
@@
 
-\subsection{Controll Group Female vs Error Group Female}
-\begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+\subsection{Control Group(50f) vs Error Group(50f)}
+\begin{figure}[!h]
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50f) and
+        the upper and lower quartile of points earned by the control group (50f) and
         the error group (50f).The green line marks the mean of all datapoints in the group.
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50f) the error group (50f).
+    for the control group (50f) the error group (50f).
     The t,p-values were calculated by using a two-sided t-test.}
@@
 
-\subsection{Controll Group Male vs Error Group Male }
+\subsection{Control Group(50m) vs Error Group(50m) }
 \begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50m) and
+        the upper and lower quartile of points earned by the control group (50m) and
         the error group (50m).The green line marks the mean of all datapoints in the group.
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50m) the error group (50m).
+    for the control group (50m) the error group (50m).
     The t,p-values were calculated by using a two-sided t-test.}
@@
 
-\subsection{Controll Group vs Error Group}
+\subsection{Control Group(50f) vs Control Group(50m)}
 \begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50f) and
-        the controll group (50m).The green line marks the mean of all datapoints in the group.
+        the upper and lower quartile of points earned by the control group (50f) and
+        the control group (50m).The green line marks the mean of all datapoints in the group.
         The gray line marks the median  of the given group.} \label{fig5}
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50f) the controll group (50m).
+    for the control group (50f) the control group (50m).
     The t,p-values were calculated by using a two-sided t-test.}
@@
         \hline
-        & controll group(f) & controll group(m) \\
+        & control group(f) & control group(m) \\
         \hline
@@
 \end{figure}
-
-\subsection{Controll Group vs Error Group}
+\clearpage
+\subsection{Error Group(50f) vs Error Group(50m)}
 \begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
@@
 
-\subsection{Controll Group vs Error Group}
+\subsection{Control Group(50f) vs Error Group(50m)}
 \begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50f) and
+        the upper and lower quartile of points earned by the control group (50f) and
         the error group (50m).The green line marks the mean of all datapoints in the group.
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50f) the error group (50m).
+    for the control group (50f) the error group (50m).
     The t,p-values were calculated by using a two-sided t-test.}
@@
 \end{figure}
-
-\subsection{Controll Group vs Error Group}
+\clearpage
+\subsection{Control Group(50m) vs Error Group(50f)}
 \begin{figure}
-    \begin{minipage}{0.45\textwidth}        
+    \begin{minipage}{0.43\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
         \caption{The colored squares in the boxplot displays
-        the upper and lower quartile of points earned by the controll group (50m) and
+        the upper and lower quartile of points earned by the control group (50m) and
         the error group (50f).The green line marks the mean of all datapoints in the group.
@@
 \hfill
-\begin{minipage}{0.45\textwidth}
+\begin{minipage}{0.43\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
-    for the controll group (50m) the error group (50f).
+    for the control group (50m) the error group (50f).
     The t,p-values were calculated by using a two-sided t-test.}
@@
 \section{Discussion}
+The collected data is very clear. Network problems do not affect students academic performance
+in a statistically firm manner.\\\\
+
+The results can not be transposed on younger students.
+Since younger students might be unable to read properly or lack experience with problem solving
+in general. Futhermore can the data not be used to make an estimate for students with disabilitys.
+However the performance of older students should be similar to the tested students.\\\\
+
+The study can make a general statement on network problems. However not all possible
+problems are simulated. It is possible that a problem exists that does affect the academic performance of
+students significantly. Futhermore designflaws of the eLearning-Environment
+or limited to no access to a computer are problems that are overlooked or ignored. These problems
+require additional studys.
 \section{Conclusion}
+
 \section{Refernces}

### 2021-07-08 Addition.tex
Update Addition.tex

@@
 
-\title{The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}}
+\title{The effect of common network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}}
 
@@
 \end{figure}
-
+\newpage
 \subsection*{Implementation}
@@
 at \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}.
+\begin{figure}[h]
+    \includegraphics[width=\textwidth]{imp.PNG}
+    \caption{The REST API}
+\end{figure}
 \subsection*{Participants}

### 2021-07-08 Draft.tex
Very close to done

@@
 
-\renewcommand\UrlFont{\color{blue}\rmfamily}
+%\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 
-\title{The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}}
+\title{The effect of commen network problems on students academic performance in an elearning-Environment
+\thanks{Supported by Goethe University Frankfurt a. Main}}
 
@@
 \section{Materials and Methodes}
+\subsection{Summary}
+To which extend do commen networks problems in an eLearning-Environment
+influence the academic performance of students. This information can be used to
+re-evaluate the eLearning-Environment.
+
 \subsection{Participants}
@@
 It should be ensured that both groups prior to the experiment perform academicly similar, if not a
-comparison post experiment will be difficult. Students of the 5th grade have the benefit of the
+comparison post experiment will be difficult. Students of the end of the 4th grade have the benefit of the
 already finished primary school. Which ensures experience in simple problem solving and
 reading comprehension. Futhermore in 4th grade we can still observe all academic capabilitys
-since the division of students happens in 5th grade.
+since the division of students happens in 5th grade. Also primary school has the least differences
+in the curriculum between the federal stats.
 
@@
 The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
-This software allowed the tracking of {\itshape technical problems} introduced by
+This software\cite{ref_soft} allowed the tracking of {\itshape technical problems} introduced by
 the software itself as well as the points and answers scored by each participant.
-Additianaly a room with an adequat number of computers with a fiber-connection
+A maximum of 100 points could be scored, these were needed to evaluate the performance of
+the students. Anymore name, gender, age, email, username and password were collected.
+These parameters were used to identify students and for futher analysis.
+Other solutions which involed already existing softwaresuits were abandon due to lack
+of customization.Additianaly a room with an adequat number of computers with a fiber-connection
 to the server are needed, to rule out uncontrolled network problems.
@@
 use of the software.
+
+\subsection{}
 
@@
 The collected data is very clear. Network problems do not affect students academic performance
-in a statistically firm manner.\\\\
+in a statistically firm manner.
 
@@
 in general. Futhermore can the data not be used to make an estimate for students with disabilitys.
-However the performance of older students should be similar to the tested students.\\\\
+However the performance of older students should be similar to the tested students.
 
@@
 problems are simulated. It is possible that a problem exists that does affect the academic performance of
-students significantly. Futhermore designflaws of the eLearning-Environment
-or limited to no access to a computer are problems that are overlooked or ignored. These problems
-require additional studys.
+students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
+Futhermore designflaws of the eLearning-Environment or limited to no access to a computer are problems that
+are overlooked or ignored. These problems require additional studys.
 \section{Conclusion}
-
+In this paper we could clearly see the impact of platform-issues on the students performance in an 
+exam-scenario and it is not significant. There might still be certain aspect of long-term-effects,
+which we couldn't simulate due to our test setup, because there was a slight worsening happening 
+when comparing our outcomes. It would be very interesting to see, how much significance such things 
+like errors will show  in a long run with more variables included.
 \section{Refernces}
+\begin{thebibliography}{8}
+    \bibitem{ref_soft}
+    Github, \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}. Last accessed 8 Jul 2021
+    \end{thebibliography}
 \end{document}

### 2021-07-08 Draft.tex
Bin durch

@@
 it's important to know the things that come with being on such a platform and the 
-possible influences those things might have on the method.\\\\
+possible influences those things might have on the method.\\
 
@@
 which extent these problems can influence the test-results of being on such an 
-'issue-infected' platform in contrast to a well running platform with no issues.\\\\
+'issue-infected' platform in contrast to a well running platform with no issues.\\
 
-We tried to focus on the most frequent issues we faced in our experience of browsing 
-on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
-(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
-\newpage
+We focused on commen network issues.Which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
+(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.
 \section{Materials and Methodes}
@@
 
-\subsection{}
+\subsection{Procedure}
+The participants are welcomed and thanked for their time.
+The students were randomly selected for either the controll group or the test group
+prospective known as the error group. Then the students where placed infront of a computer
+which was either manipulated or untouched based on their group.They then create an account
+and start solving the questions.
+After they finished all questions they log out.
+The students are rewarded with cookies and again thanked for their time.
 
@@
 \end{figure}
-
-\clearpage
+\newpage
 \section{Results}
 The results are displayed in chronological order of the analysis, there is
-no emphisis on the significans given by the order itself.
+no emphisis on the significans given by the order itself. The following data is
+what we would expect in an actual experiment. To recreate the data see \cite{ref_soft}.
 
@@
 \begin{figure}[!h]
-    \begin{minipage}{0.43\textwidth}        
+    \begin{minipage}{0.4\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
@@
 \hfill
-\begin{minipage}{0.43\textwidth}
+\begin{minipage}{0.4\textwidth}
 \captionof{table}{The calculated median, standart deviation and t, p-values
@@
 \subsection{Control Group(50f) vs Error Group(50f)}
-\begin{figure}[!h]
-    \begin{minipage}{0.43\textwidth}        
+\begin{figure}[!ht]
+    \begin{minipage}{0.4\textwidth}        
         \includegraphics[width=\textwidth]{code/generate/all.png}
@@
 \subsection{Control Group(50m) vs Error Group(50m) }
-\begin{figure}
+\begin{figure}[!h]
     \begin{minipage}{0.43\textwidth}        
@@
 students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
-Futhermore designflaws of the eLearning-Environment or limited to no access to a computer are problems that
-are overlooked or ignored. These problems require additional studys.
+Futhermore designflaws of the eLearning-Environment are also overlooked or ignored.
+These problems require additional studys.
 \section{Conclusion}
@@
 which we couldn't simulate due to our test setup, because there was a slight worsening happening 
-when comparing our outcomes. It would be very interesting to see, how much significance such things 
-like errors will show  in a long run with more variables included.
+when comparing our outcomes. Futher studys should focus on the longterm effect of technical problems
+to deepen our understanding of the technology.
 \section{Refernces}

### 2021-07-08 Addition.tex

@@
 \section{Conclusion}
-In this paper we could clearly see the impact of platform-issues on the students performance in an exam-scenario and it's not that significant.
-There might still be certain aspect of long-term-effects,
+In this paper we can clearly see the impact of platform-issues on the students performance in an exam-scenario and it's not that significant. There might still be certain aspect of long-term-effects,
 which we couldn't simulate due to our circumstances, because there was a slight worsening happening when comparing our outcomes.

### 2021-07-08 Draft.tex
Update Draft.tex

@@
 
-\title{The effect of commen network problems on students academic performance in an elearning-Environment
+\title{The effect of common network problems on students academic performance in an elearning-Environment
 \thanks{Supported by Goethe University Frankfurt a. Main}}
@@
 of eLearning-Software experienced an unpresented boom.
-We state the question how commen network problems influence
+We state the question how common network problems influence
 the academic performance in an eLearning-Environment.
@@
 
-We focused on commen network issues.Which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
+We focused on common network issues.Which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
 (Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.
-\section{Materials and Methodes}
+\section{Materials and Methods}
 \subsection{Summary}
-To which extend do commen networks problems in an eLearning-Environment
+To which extend do common networks problems in an eLearning-Environment
 influence the academic performance of students. This information can be used to
@@
 the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
-It should be ensured that both groups prior to the experiment perform academicly similar, if not a
+It should be ensured that both groups prior to the experiment perform academically similar, if not a
 comparison post experiment will be difficult. Students of the end of the 4th grade have the benefit of the
 already finished primary school. Which ensures experience in simple problem solving and
-reading comprehension. Futhermore in 4th grade we can still observe all academic capabilitys
+reading comprehension. Furthermore in 4th grade we can still observe all academic capabilities
 since the division of students happens in 5th grade. Also primary school has the least differences
@@
 
-\subsection{Preperations}
+\subsection{Preparations}
 The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
@@
 the students. Anymore name, gender, age, email, username and password were collected.
-These parameters were used to identify students and for futher analysis.
-Other solutions which involed already existing softwaresuits were abandon due to lack
-of customization.Additianaly a room with an adequat number of computers with a fiber-connection
+These parameters were used to identify students and for further analysis.
+Other solutions which involved already existing software-suits were abandon due to lack
+of customization.Additionally a room with an adequate number of computers with a fiber-connection
 to the server are needed, to rule out uncontrolled network problems.
-Half of the cumputers are manipulated and simulate the network problems with the
+Half of the computers are manipulated and simulate the network problems with the
 use of the software.
@@
 The participants are welcomed and thanked for their time.
-The students were randomly selected for either the controll group or the test group
-prospective known as the error group. Then the students where placed infront of a computer
+The students were randomly selected for either the control group or the test group
+prospective known as the error group. Then the students where placed in front of a computer
 which was either manipulated or untouched based on their group.They then create an account
@@
     \caption{A logic flow chart , representing how an implementation could operate.
-    The black circle is the user interacting with the software. The webside would
-    consist of two parts. A frontend handling user interaction and the creation of {\itshape bugs}.
-    The backend responsible for saving the collected data and ensuring the frontend
-    remains operationale.} \label{fig1}
+    The black circle is the user interacting with the software. The website would
+    consist of two parts. A front-end handling user interaction and the creation of {\itshape bugs}.
+    The back-end responsible for saving the collected data and ensuring the front-end
+    remains operational.} \label{fig1}
 \end{figure}
@@
 The results are displayed in chronological order of the analysis, there is
-no emphisis on the significans given by the order itself. The following data is
+no emphasis on the significance given by the order itself. The following data is
 what we would expect in an actual experiment. To recreate the data see \cite{ref_soft}.
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50f/50m) and
-        the error group (50f/50m).The green line marks the mean of all datapoints in the group.
+        the error group (50f/50m).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig2}
@@
 \begin{minipage}{0.4\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50f/50m) the error group (50f/50m).
@@
         \hline
-        standart deviation & 29.278&29.826 \\
+        standard deviation & 29.278&29.826 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50f) and
-        the error group (50f).The green line marks the mean of all datapoints in the group.
+        the error group (50f).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig3}
@@
 \begin{minipage}{0.4\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50f) the error group (50f).
@@
         \hline
-        standart deviation & 27.85&30.933 \\
+        standard deviation & 27.85&30.933 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50m) and
-        the error group (50m).The green line marks the mean of all datapoints in the group.
+        the error group (50m).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig4}
@@
 \begin{minipage}{0.43\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50m) the error group (50m).
@@
         \hline
-        standart deviation & 30.638&28.495 \\
+        standard deviation & 30.638&28.495 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50f) and
-        the control group (50m).The green line marks the mean of all datapoints in the group.
+        the control group (50m).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig5}
@@
 \begin{minipage}{0.43\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50f) the control group (50m).
@@
         \hline
-        standart deviation & 27.85&30.638 \\
+        standard deviation & 27.85&30.638 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the error group (50f) and
-        the error group (50m).The green line marks the mean of all datapoints in the group.
+        the error group (50m).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig6}
@@
 \begin{minipage}{0.43\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the error group (50f) the error group (50m).
@@
         \hline
-        standart deviation & 30.933&28.495 \\
+        standard deviation & 30.933&28.495 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50f) and
-        the error group (50m).The green line marks the mean of all datapoints in the group.
+        the error group (50m).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig7}
@@
 \begin{minipage}{0.43\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50f) the error group (50m).
@@
         \hline
-        standart deviation & 27.85&28.495 \\
+        standard deviation & 27.85&28.495 \\
         \hline
@@
         \includegraphics[width=\textwidth]{code/generate/all.png}
-        \caption{The colored squares in the boxplot displays
+        \caption{The colored squares in the box-plot displays
         the upper and lower quartile of points earned by the control group (50m) and
-        the error group (50f).The green line marks the mean of all datapoints in the group.
+        the error group (50f).The green line marks the mean of all data-points in the group.
         The gray line marks the median  of the given group.} \label{fig8}
@@
 \begin{minipage}{0.43\textwidth}
-\captionof{table}{The calculated median, standart deviation and t, p-values
+\captionof{table}{The calculated median, standard deviation and t, p-values
     for the control group (50m) the error group (50f).
@@
         \hline
-        standart deviation & 30.638&30.933 \\
+        standard deviation & 30.638&30.933 \\
         \hline
@@
 Since younger students might be unable to read properly or lack experience with problem solving
-in general. Futhermore can the data not be used to make an estimate for students with disabilitys.
+in general. Furthermore can the data not be used to make an estimate for students with disabilities.
 However the performance of older students should be similar to the tested students.
@@
 problems are simulated. It is possible that a problem exists that does affect the academic performance of
-students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
-Futhermore designflaws of the eLearning-Environment are also overlooked or ignored.
-These problems require additional studys.
+students significantly. Also long-term effects can not be discovered by this study since it is very time limited.
+Furthermore design-flaws of the eLearning-Environment are also overlooked or ignored.
+These problems require additional studies.
 \section{Conclusion}
@@
 which we couldn't simulate due to our test setup, because there was a slight worsening happening 
-when comparing our outcomes. Futher studys should focus on the longterm effect of technical problems
-to deepen our understanding of the technology.
-\section{Refernces}
+when comparing our outcomes. Further studies should focus on the long-term effect of technical problems to deepen our understanding of the technology.
+\section{References}
 \begin{thebibliography}{8}
